

\begin{flashcard}[Definition]{Subset}
  Notation: $A \subseteq B$, informally $A \subset B$
  \vfill
  if $x \in A$, then $x \in B$
\end{flashcard}

\begin{flashcard}[Definition]{Proper Subet}
  Notation: $A \subset B$
  \vfill
  $A \subseteq B$ and $A \neq B$
\end{flashcard}

\begin{flashcard}[Definition]{Union}
  Notation: $A \cup B$
  \vfill
  $\{x \mid x \in A \text{ or } x \in B\}$
\end{flashcard}

\begin{flashcard}[Definition]{Intersection}
  Notation: $A \cap B$
  \vfill
  $\{x \mid x \in A \text{ and } x \in B\}$
\end{flashcard}

\begin{flashcard}[Definition]{Disjoint Sets}
  A and B are disjoint if $A \cap B = \O$
\end{flashcard}

\begin{flashcard}[Definition]{Equal Sets}
  A and B are equivalent if $A \subset B$ and $B \subset A$
\end{flashcard}

\begin{flashcard}[Definition]{Complement}
  For any set $A \subset U$
  \vfill
  $A' = \{x \in U \mid x \notin A \}$
\end{flashcard}

\begin{flashcard}[Definition]{Difference}
  $A \setminus B = A \cap B'$
\end{flashcard}

\begin{flashcard}[Definition]{Cartesian Product}
  $A \bigtimes B = \{ (a,b) \mid a \in A \text{ and } b \in B \}$
\end{flashcard}

\begin{flashcard}[Definition]{Relation}
  A relation from A to B is a subset of $A \bigtimes B$
\end{flashcard}

\begin{flashcard}[Definition]{Function or Map}
  Notation: $f: A \to B$, where A is the \emph{domain} and B is the \emph{target}
  \vfill
  A relation from A to B where $\forall a \in A, \exists!\ (a,b)$
  \vfill
  $f(a) = b$ means $(a,b) \in f$
\end{flashcard}

\begin{flashcard}[Definition]{Image of Function}
  $f(A) = \{f(a): a \in A\}$
  \vfill
  Note: $f(A) \subset B$
\end{flashcard}

\begin{flashcard}[Definition]{Surjective}
  Also known as \emph{onto}
  \vfill
  A function $f: A \to B$ for which $f(A) = B$
\end{flashcard}

\begin{flashcard}[Definition]{Injective}
  Also known as \emph{one-to-one}
  \vfill
  A function $f: A \to B$ for which $f(a_1) = f(a_2)$ implies $a_1 = a_2$
\end{flashcard}

\begin{flashcard}[Definition]{Bijective}
  A function which is both injective and surjective.
\end{flashcard}

\begin{flashcard}[Definition]{Composition}
  For $f: A \to B$ and $g: B \to C$ , the composition~$g \circ f$ is defined as:
  \vfill
  $(g \circ f)(x) = g(f(x))$
  \vfill
  Notes: $g \circ f: A \to C$, and composition is associative
\end{flashcard}

\begin{flashcard}[Definition]{Composition Properties}
  \begin{itemize}
    \item If g and f are surjective, $g \circ f$ is surjective
    \item If g and f are injective, $g \circ f$ is injective
    \item If g and f are bijective, $g \circ f$ is bijective
  \end{itemize}
\end{flashcard}

\begin{flashcard}[Definition]{Identity Map}
  Notation: $id_s$
  \vfill
  $id(x) = x, id: S \to S$
  \vfill
  Note: $id_s = \{ (x,x): x \in S \}$
\end{flashcard}

\begin{flashcard}[Definition]{Inverse}
  Notation: $\inv{f}$
  \vfill
  $g = \inv{f} \iff g \circ f = id_A$
  \vfill
  $f$ is invertible means it has an inverse.
  \vfill
  $f$ is invertible iff it's bijective.
\end{flashcard}

\begin{flashcard}[Definition]{Partition}
  Let X be a set. P is a partition of X means:
  \vfill
  $P = \{ p_i \subset X \mid P \neq \O \}$, all $p_i$ are disjoint, and the union of all $p_i$ is P.
\end{flashcard}

\begin{flashcard}[Definition]{Equivalence Relation}
  Relation R of X with these properties:
  \begin{itemize}
    \item Reflexive:  $\forall x \in X, (x,x) \in R$
    \item Symmetric:  $(x,y) \in R \implies (y,x) \in R$
    \item Transitive: $(x,y), (y,z) \in R \implies (x,z) \in R$
  \end{itemize}
  $x \sim y$ means $(x,y) \in R$
\end{flashcard}

\begin{flashcard}[Definition]{Equivalence Class}
  $[x] = \{y \in X \mid y \sim x\}$
  \vfill
  Two equivalence classes are either disjoint or equal.
\end{flashcard}

\begin{flashcard}[Definition]{Divisibility}
  Notation: $b \mid a$ (b divides a)
  \vfill
  $a = bk$ for some $k \in \Z$
\end{flashcard}

\begin{flashcard}[Definition]{Congruence}
  Let $r,s \in \Z$ and $n \in \N$.
  \vfill
  Notation: $r \equiv_n s$
  \vfill
  $n \mid (r - s)$
  \vfill
  Note: $\equiv_n$ is an equivalence relation of $\Z$
\end{flashcard}

\begin{flashcard}[Definition]{Properties of Congruence}
  \begin{itemize}
    \item $a + b \equiv b + a$ \quad $ab \equiv ba$
    \item $(a + b) + c \equiv a + (b + c)$ \quad  $(ab)c \equiv a(bc)$
    \item $a + 0 \equiv a$ \quad $a1 \equiv a$
    \item Multiplication distributes over addition
    \item $\exists b \in \Z \mid a + b \equiv 0 $
    \item Let $a \in \Z, a \neq 0$
      \newline
      $gcd(a,n) = 1 \iff \exists b \in \Z \mid ab \equiv_n 1$
  \end{itemize}
\end{flashcard}

\begin{flashcard}[Definition]{Mathematical Induction}
  Let $S(n)$ be a statement about $n \in \N$
  \vfill
  If $S(n_0)$ is true for some $n_0 \in \N$, and $S(k) \implies S(k+1)$, then $S(n)$ is true for all $n \geq n_0$
\end{flashcard}

\begin{flashcard}[Definition]{Strong Mathematical Induction}
  Let $S(n)$ be a statement about $n \in \N$
  \vfill
  If $S(n_0)$ is true for some $n_0 \in \N$, and $S(n_0), S(n_0 + 1), S(n_0+2) \dots S(k) \implies S(k+1)$, then $S(n)$ is true for all $n \geq n_0$
\end{flashcard}

\begin{flashcard}[Definition]{Well-Ordered}
  A non-empty subset of $\Z$ which contains a least element.
\end{flashcard}

\begin{flashcard}[Definition]{Well-Ordering Principle}
  Every non-empty subset of $\N$ is well-ordered.
\end{flashcard}

\begin{flashcard}[Definition]{Division Algorithm}
  Let $a,b \in \Z$ and $b > 0$
  \vfill
  $\exists!\ q,r \in \Z \mid a = qb + r$ and $0 \leq r < b$
\end{flashcard}

\begin{flashcard}[Definition]{Common Divisor}
  Let $a,b,d \in \Z$
  \vfill
  d is a common divisor of a and b means that $d \mid a$ and $d \mid b$
\end{flashcard}

\begin{flashcard}[Definition]{Greatest Common Divisor}
  Notation: $gcd(a,b)$ where $a,b \in \Z$
  \vfill
  Note: If $a,b > 0,\ \exists r,s \in \Z \mid gcd(a,b) = ar + bs$
\end{flashcard}

\begin{flashcard}[Definition]{Relatively Prime}
  $gcd(a,b) = 1$
\end{flashcard}

\begin{flashcard}[Definition]{Prime}
  p is prime if only numbers that divide it are 1 and p
  \vfill
  Otherwise, p is \emph{composite}
\end{flashcard}

\begin{flashcard}[Definition]{Prime Number Properties}
  $p \mid ab \implies p \mid a \text{ or } p \mid b$
  \vfill
  There exists an infinite number of primes.
\end{flashcard}

\begin{flashcard}[Definition]{Fundamental Theorem of Arithmetic}
  Let $n \in \N, n > 1$
  \vfill
  $n = p_1p_2p_3 \dots p_k$ where $p_i$ are prime
  \vfill
  This factorization is unique.
\end{flashcard}

\begin{flashcard}[Definition]{Binary Operation}
  A function $f: S \bigtimes S \to S$ on a set S
  \vfill
  $f(a,b)$ is denoted by $a \circ b$ or  $ab$
\end{flashcard}

\begin{flashcard}[Definition]{Group}
  Notation: $(S, \circ)$ for operation $\circ$ on set S
  \vfill
  Properties:
  \begin{itemize}
    \item Associative: $(ab)c = a(bc)$
    \item Identity Exists: $\exists e \in S \mid ai = a = ia, \forall a \in S$
    \item Inverses Exist: $\forall a \in S, \exists b \in S \mid ab = e = be$
  \end{itemize}
\end{flashcard}

\begin{flashcard}[Definition]{Group Properties}
  The inverses are unique for each element.
  \vfill
  $\inv{(ab)} = \inv{a}\inv{b}$
\end{flashcard}

\begin{flashcard}[Definition]{Commutative/Abelian Group}
  A group for which $ab = ba\ \forall a,b \in S$
\end{flashcard}

\begin{flashcard}[Definition]{Finite Group}
  $(G,\circ)$ is a finite group if G is a finite set.
  \vfill
  Otherwise, it's an infinite group.
\end{flashcard}

\begin{flashcard}[Definition]{Group Order}
  The order of finite group $(G,\circ)$ is $\mid G \mid$.
  \vfill
  The order of an infinite group is $\infty$.
\end{flashcard}

\begin{flashcard}[Definition]{Quaternion Group}
  $(Q_8, \circ)$ where $Q_8 = \{\pm 1, \pm i, \pm j, \pm k\}$ and:
  \begin{itemize}
    \item $i^2 = j^2 = k^2 = -1$
    \item 1 is identity
    \item -1 commutes everything
    \item $ij = k, jk = i, ki = j$
    \item $ik = -j, kj = -i, ji = -k$
  \end{itemize}
\end{flashcard}

\begin{flashcard}[Definition]{Matrix Group}
  $\M_2(\R)$ is multiplicative group for all 2x2 real number matrices.
  \vfill
  Non-abelian group.
\end{flashcard}

\begin{flashcard}[Definition]{General Linear Group}
  $GL_2(\R)$ is subset of $\M_2(\R)$ where every matrix is invertible.
  \vfill
  Non-abelian group.
\end{flashcard}

\begin{flashcard}[Definition]{Multiplicative Group Exponents}
  \begin{itemize}
    \item $g^n = g \circ g \circ g \circ g \dots \mid n \geq 1$
    \item $g^0 = e$
    \item $g^{-1} = \inv{g} \circ \inv{g} \circ \inv{g} \dots \mid n < 0$
    \item $g^mg^n = g^{m+n}$, $(g^m)^n = g^{mn}$
    \item $(gh)^n = (\inv{h}\inv{g})^{-n}$
  \end{itemize}
  \vfill
  If group is abelian, then $(gh)^n = g^nh^n$
\end{flashcard}

\begin{flashcard}[Definition]{Additive Group Exponents}
  \begin{itemize}
    \item $ng = g + g + g \dots \mid n \geq 0$
    \item $-ng = -g + -g + -g \dots \mid n < 0$
  \end{itemize}
  \vfill
  If group is abelian, then $m(g + h) = mg + mh$
\end{flashcard}

\begin{flashcard}[Definition]{Group Cancellation Laws}
  If G is a group, and $a,b,c \in G$, then:
  \vfill
  $ba = bc \implies a = c$ (left cancellation)
  \vfill
  $ab = cb \implies a = c$ (right cancellation)
\end{flashcard}

\begin{flashcard}[Definition]{Subgroup}
  A group $(H, \circ)$ is a subgroup of $(G, \circ)$ if $H \subseteq G$ and if H also forms a group under the operation~$\circ$. This is true iff:
  \vfill
  \begin{itemize}
   \item Identity $e \in G$ is in H
   \item $h_1,h_2 \in H \implies h_1 \circ h_2 \in H$
   \item $h_1 \in H \implies \inv{h_1} \in H$
  \end{itemize}
\end{flashcard}

\begin{flashcard}[Definition]{Subgroup Alternative Criteria}
  Let $H \subseteq G$. H is a subgroup of G iff:
  \vfill
  \begin{itemize}
   \item $H \neq \O$
   \item $a,b \in H \implies a \circ \inv{b} \in H$
  \end{itemize}
\end{flashcard}

\begin{flashcard}[Definition]{Trivial Subgroup}
  $\{e\}$
\end{flashcard}

\begin{flashcard}[Definition]{Proper Subgroup}
  H is a proper subgroup of G if H is a subgroup, and $H \subset G$
\end{flashcard}

\begin{flashcard}[Definition]{Cyclic Subgroup}
  $\gen{g}$ is the cyclic subgroup of G generated by $g \in G$
  \vfill
  $\gen{g} = \{ g^n \mid n \in \Z \}$
  \vfill
  g is the generator of $\gen{g}$
  \vfill
  $\gen{g}$ is the smallest subgroup of G containing g
\end{flashcard}

\begin{flashcard}[Definition]{Order of Generator}
  Order $\mid{g}\mid$ is the smallest $n \in \N \mid g^n = e$
  \vfill
  If none exist, $\mid{g}\mid = \infty$
\end{flashcard}

\begin{flashcard}[Definition]{Cyclic Group}
  G is a cyclic group if $\exists\,g \in G \mid G =\, \gen{g}$
\end{flashcard}

\begin{flashcard}[Definition]{Cyclic Group Properties}
  Every cyclic group is abelian.
  \vfill
  Let $G = \gen{x}$, \quad $x^k = e \iff n \mid k$
  \vfill
  Every subgroup of a cyclic group is cyclic.
  \vfill
  For cyclic group G of order n, and a generating~$\gen{a}$, \quad $b = a^k \implies \mid b \mid = \frac{n}{gcd(k,n)}$
\end{flashcard}

\begin{flashcard}[Definition]{Finite Cyclic Group in $\Z$}
  Let $Z_n = \{ 0,1,2,3,4, \dots , n - 1 \}$
  \vfill
  $(Z_n, +)$ is an abelian group such that:
  \vfill
  $a + b = c$ where $a + b \equiv_n c$
\end{flashcard}

\begin{flashcard}[Definition]{Group of Units}
  $U_n = \{ m \mid 1 \leq m < n,\ gcd(m,n) = 1 \}$
\end{flashcard}

\begin{flashcard}[Definition]{Permutation}
  A permutation of a set X is a bijective map $f: X \to X$
  \vfill
  Notation: \[
    \bigl(\begin{smallmatrix}
      A\ B\ C \\ B\ A\ C
    \end{smallmatrix}\bigr)
  \]
\end{flashcard}

\begin{flashcard}[Definition]{Symmetric Group}
  All permutations of a set X.
  \vfill
  $S_n$ (or $S_X$) for set X or order n.
  \vfill
  Binary operation is function composition.
  \vfill
  Note: $\mid S_n \mid = n!$
\end{flashcard}

\begin{flashcard}[Definition]{Permutation Group}
  Subgroup of a symmetric group.
  \vfill
  Not usually abelian.
\end{flashcard}

\begin{flashcard}[Definition]{Cycle}
  A permutation $p \in S_X$ such that $\exists a_1 a_2 a_3 \dots  a_n \in X$ and:
  \vfill
  $p(a_1) = a_2$ \\
  $p(a_2) = a_3$ \\
  \dots \\
  $p(a_n) = a_1$
  \vfill
  Notation: $(a_1 a_2 a_3 \dots a_n)$ for an \emph{n-}cycle
\end{flashcard}

\begin{flashcard}[Definition]{Disjoint Cycles}
  Two cycles $(a_1 a_2 a_3 \dots a_n)$ and $(b_1 b_2 b_3 \dots b_m)$ are disjoint if $a_j \neq b_k$ for all $j \in [1,n]$ and $k \in [1,m]$.
\end{flashcard}

\begin{flashcard}[Definition]{Transposition}
  A cycle of length 2
\end{flashcard}

\begin{flashcard}[Definition]{Cycles Properties}
  Every permutation in $S_n$ can be written as a product of disjoint cycles.
  \vfill
  The product of disjoint cycles cannot be simplified to smaller disjoint cycles.
  \vfill
  Disjoint cycles are commutative.
  \vfill
  Every cycle can be written as the product of transpositions.
\end{flashcard}

\begin{flashcard}[Definition]{Alternating Groups}
  $A_n$ is alternating group on n letters.
  \vfill
  Subgroup of $S_n$ with all even permutations.
  \vfill
  Order $|S_n|/2$
\end{flashcard}

\begin{flashcard}[Definition]{Dihedral Group}
  $D_n = \{ r_0, r_1, r_2, \dots, r_{n-1}, s_1, s_2, \dots, s_n \} $
  \vfill
  The $n^{th}$ dihedral group. Rigid motions of n-gon. Subgroup of $S_n$.
  \vfill
  $s^2 = 1, \  r^n = 1, \  srs = \inv{r}$
\end{flashcard}

\begin{flashcard}[Definition]{Motion Group of Cube}
  24 elements
  \vfill
  Made up of all rotations around midpoint diagonals.
  \vfill
  Isomorphic to $S_4$
\end{flashcard}

\begin{flashcard}[Definition]{Complex Numbers}
  $\C = \{ a + bi \mid a,b \in \R \}$
\end{flashcard}

\begin{flashcard}[Definition]{Complex Conjugate}
  $\overline{z} = a - bi$
\end{flashcard}

\begin{flashcard}[Definition]{Absolute Value of Complex Number}
  $|z| = \sqrt{a^2 + b^2}$
\end{flashcard}

\begin{flashcard}[Definition]{Inverse of Complex Number}
  $\inv{z} = \ddfrac{z\overline{z}}{|z|^2}$
\end{flashcard}

\begin{flashcard}[Definition]{Complex Number Polar Coordinates}
  $a + bi = r cis(\theta)$
\end{flashcard}

\begin{flashcard}[Definition]{cis}
  $cis(\theta) = cos(\theta) + isin(\theta)$
\end{flashcard}

\begin{flashcard}[Definition]{Polar Complex Number Multiplication}
  Let $z = rcis(\theta) \quad w = scis(\phi) \quad z,w \neq 0$
  \vfill
  $wz = rscis(\theta + \phi)$
\end{flashcard}

\begin{flashcard}[Definition]{De Moivre Theorem}
  Let $z = rcis(\theta) \quad z \neq 0$
  \vfill
  $(rcis(\theta))^n = r^ncis(n\theta)$ where $n \in \N$
\end{flashcard}

\begin{flashcard}[Definition]{Circle Group}
  $\T = \{ z \in \C : |z| = 1 \}$
  \vfill
  $\T$ is a subgroup of $\C^*$
  \vfill
  $|T|$ is infinite
\end{flashcard}

\begin{flashcard}[Definition]{Roots of Unity}
  Elements of $\T$ satisfying $z^n = 1$ are the $n^{th}$ roots of unity.
  \vfill
  $z = cis(\frac{2k\pi}{n}) \mid k \in \{ 0, 1, 2, \dots, n-1 \}$
  \vfill
  Cyclic subgroup of $\T$ of order n. A generator is a primitive $n^{th}$ root of unity.
\end{flashcard}

\begin{flashcard}[Definition]{Coset}
  Let H be a subgroup of G.
  \vfill
  $gH = \{ gh \mid h \in H \}$ (left coset) \smallskip
  $Hg = \{ hg \mid h \in H \}$ (right coset)
  \vfill
  If gH = Hg, they're cosets.
  \vfill
  g is a representative of the coset.
\end{flashcard}

\begin{flashcard}[Definition]{Coset Properties}
  The number of left and right cosets of H in G are equal.
  \vfill
  The left/right cosets of H in G form a partition of G.
\end{flashcard}

\begin{flashcard}[Definition]{Coset Equivalences}
  For $g_1, g_2 \in G$, the following are equivalent:
  \begin{itemize}
    \item $g_1 H = g_2 H$
    \item $H \inv{g_1} = H \inv{g_2}$
    \item $g_1 H \subset g_2 H$
    \item $g_2 \in g_1 H$
    \item $\inv{g_1}g_2 \in H$
  \end{itemize}
\end{flashcard}

\begin{flashcard}[Definition]{Index}
  $[G : H]$ is index of H in G
  \vfill
  Number of left/right cosets of H in G.
\end{flashcard}

\begin{flashcard}[Definition]{Well-Defined}
  A function whos value is independent of the choice of representation of the input.
\end{flashcard}
